Graph embedding and transfer learning can help predict potential species interaction networks despite data limitations

### 2023-09-02 index.qmd
wup

---
title: Graph embedding and transfer learning can help predict potential species interaction networks despite data limitations
authors:
  - name: Tanya Strydom
    affiliation:
        - ref: udem
        - ref: qcbs
    orcid: 0000-0001-6067-1349
    email: tanya.strydom@umontreal.ca
  - name: Salomé Bouskila
    affiliation:
        - ref: udem
    roles: writing
    corresponding: false
    orcid: 0000-0003-0193-5441
    email: salome.bouskila@umontreal.ca
  - name: Francis Banville
    affiliation:
        - ref: udem
        - ref: qcbs
        - ref: udes
    orcid: 0000-0001-9051-0597
    email: francis.banville@umontreal.ca
  - name: Ceres Barros
    affiliation:
        - ref: ubcforest
    orcid: 0000-0003-4036-977X
    email: cbarros@mail.ubc.ca
  - name: Dominique Caron
    affiliation:
        - ref: mcgill
        - ref: qcbs
    orcid: 0000-0002-2151-6693
    email: dominique.caron@mail.mcgill.ca
  - name: Maxwell J. Farrell
    affiliation:
        - ref: uoft
    orcid: 0000-0003-0452-6993
    email: maxwell.farrell@utoronto.ca
  - name: Marie-Josée Fortin
    affiliation:
        - ref: uoft
    orcid: 0000-0002-9935-1366
    email: mariejosee.fortin@utoronto.ca
  - name: Victoria Hemming
    affiliation:
        - ref: ubccons
    orcid: 0000-0003-3220-6161
    email: victoria.hemming@ubc.ca
  - name: Benjamin Mercier
    affiliation:
        - ref: udes
        - ref: qcbs
    orcid: 0000-0002-4104-9463
    email: benjamin.b.mercier@usherbrooke.ca
  - name: Laura J. Pollock
    affiliation:
        - ref: mcgill
        - ref: qcbs
    orcid: 0000-0002-6004-4027
    email: laura.pollock@mcgill.ca
  - name: Rogini Runghen
    affiliation:
        - ref: ucecology
    orcid: 0000-0001-5785-8321
    email: rogini.runghen@gmail.com
  - name: Giulio V. Dalla Riva
    affiliation:
        - ref: ucmath
    orcid: 0000-0002-3454-0633
    email: giulio.dallariva@canterbury.ac.nz
  - name: Timothée Poisot
    affiliation:
        - ref: udem
        - ref: qcbs
    orcid: 0000-0002-0735-5184
    corresponding: true
    email: timothee.poisot@umontreal.ca
affiliations:
    - id: udem
      name: Département de Sciences Biologiques, Université de Montréal, Montréal, Canada
    - id: qcbs
      name: Québec Centre for Biodiversity Science, Montréal, Canada
    - id: udes
      name: Département de Biologie, Université de Sherbrooke, Sherbrooke, Canada
    - id: ubcforest
      name: Department of Forest Resources Management, University of British Columbia, Vancouver, B.C., Canada
    - id: mcgill
      name: Department of Biology, McGill University, Montréal, Canada
    - id: uoft
      name: Department of Ecology & Evolutionary Biology, University of Toronto, Toronto, Canada
    - id: ubccons
      name: Department of Forest and Conservation Sciences, University of British Columbia, Vancouver, Canada
    - id: ucecology
      name: Department of Forest and Conservation Sciences, University of British Columbia, Vancouver, Canada
    - id: ucmath
      name: Department of Forest and Conservation Sciences, University of British Columbia, Vancouver, Canada
bibliography: references.bib
---

@@

**Acknowledgements:** We acknowledge that this study was conducted on land
within the traditional unceded territory of the Saint Lawrence Iroquoian,
Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak nations. TP, TS, DC,
and LP received funding from the Canadian Institute for Ecology & Evolution. FB
is funded by the Institute for Data Valorization (IVADO). TS, SB, and TP are
funded by a donation from the Courtois Foundation. CB was awarded a Mitacs
Elevate Fellowship no. IT12391, in partnership with fRI Research, and also
acknowledges funding from Alberta Innovates and the Forest Resources Improvement
Association of Alberta. M-JF acknowledges funding from NSERC Discovery Grant and
NSERC CRC. RR is funded by New Zealand’s Biological Heritage Ngā Koiora Tuku Iho
National Science Challenge, administered by New Zealand Ministry of Business,
Innovation, and Employment. BM is funded by the NSERC Alexander Graham Bell
Canada Graduate Scholarship and the FRQNT master’s scholarship. LP acknowledges
funding from NSERC Discovery Grant (NSERC RGPIN-2019-05771). TP acknowledges
financial support from the Fondation Courtois, and NSERC through the Discovery
Grants and Discovery Accelerator Supplement programs. MJF is supported by an
NSERC PDF and an RBC Post-Doctoral Fellowship.

>>>>

---
title: Graph embedding and transfer learning can help predict potential species interaction networks despite data limitations
authors:
  - name: Tanya Strydom
    affiliation:
        - ref: udem
        - ref: qcbs
    orcid: 0000-0001-6067-1349
    email: tanya.strydom@umontreal.ca
  - name: Salomé Bouskila
    affiliation:
        - ref: udem
    roles: writing
    corresponding: false
    orcid: 0000-0003-0193-5441
    email: salome.bouskila@umontreal.ca
  - name: Francis Banville
    affiliation:
        - ref: udem
        - ref: qcbs
        - ref: udes
    orcid: 0000-0001-9051-0597
    email: francis.banville@umontreal.ca
  - name: Ceres Barros
    affiliation:
        - ref: ubcforest
    orcid: 0000-0003-4036-977X
    email: cbarros@mail.ubc.ca
  - name: Dominique Caron
    affiliation:
        - ref: mcgill
        - ref: qcbs
    orcid: 0000-0002-2151-6693
    email: dominique.caron@mail.mcgill.ca
  - name: Maxwell J. Farrell
    affiliation:
        - ref: uoft
    orcid: 0000-0003-0452-6993
    email: maxwell.farrell@utoronto.ca
  - name: Marie-Josée Fortin
    affiliation:
        - ref: uoft
    orcid: 0000-0002-9935-1366
    email: mariejosee.fortin@utoronto.ca
  - name: Benjamin Mercier
    affiliation:
        - ref: udes
        - ref: qcbs
    orcid: 0000-0002-4104-9463
    email: benjamin.b.mercier@usherbrooke.ca
  - name: Laura J. Pollock
    affiliation:
        - ref: mcgill
        - ref: qcbs
    orcid: 0000-0002-6004-4027
    email: laura.pollock@mcgill.ca
  - name: Rogini Runghen
    affiliation:
        - ref: ucecology
    orcid: 0000-0001-5785-8321
    email: rogini.runghen@gmail.com
  - name: Giulio V. Dalla Riva
    affiliation:
        - ref: ucmath
    orcid: 0000-0002-3454-0633
    email: giulio.dallariva@canterbury.ac.nz
  - name: Timothée Poisot
    affiliation:
        - ref: udem
        - ref: qcbs
    orcid: 0000-0002-0735-5184
    corresponding: true
    email: timothee.poisot@umontreal.ca
affiliations:
    - id: udem
      name: Département de Sciences Biologiques, Université de Montréal, Montréal, Canada
    - id: qcbs
      name: Québec Centre for Biodiversity Science, Montréal, Canada
    - id: udes
      name: Département de Biologie, Université de Sherbrooke, Sherbrooke, Canada
    - id: ubcforest
      name: Department of Forest Resources Management, University of British Columbia, Vancouver, B.C., Canada
    - id: mcgill
      name: Department of Biology, McGill University, Montréal, Canada
    - id: uoft
      name: Department of Ecology & Evolutionary Biology, University of Toronto, Toronto, Canada
    - id: ubccons
      name: Department of Forest and Conservation Sciences, University of British Columbia, Vancouver, Canada
    - id: ucecology
      name: Department of Forest and Conservation Sciences, University of British Columbia, Vancouver, Canada
    - id: ucmath
      name: Department of Forest and Conservation Sciences, University of British Columbia, Vancouver, Canada
bibliography: references.bib
---

@@

**Acknowledgements:** We acknowledge that this study was conducted on land
within the traditional unceded territory of the Saint Lawrence Iroquoian,
Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak nations. We thank Victoria
hemming for feedback on this manuscript. TP, TS, DC, and LP received funding from the Canadian Institute for Ecology & Evolution. FB
is funded by the Institute for Data Valorization (IVADO). TS, SB, and TP are
funded by a donation from the Courtois Foundation. CB was awarded a Mitacs
Elevate Fellowship no. IT12391, in partnership with fRI Research, and also
acknowledges funding from Alberta Innovates and the Forest Resources Improvement
Association of Alberta. M-JF acknowledges funding from NSERC Discovery Grant and
NSERC CRC. RR is funded by New Zealand’s Biological Heritage Ngā Koiora Tuku Iho
National Science Challenge, administered by New Zealand Ministry of Business,
Innovation, and Employment. BM is funded by the NSERC Alexander Graham Bell
Canada Graduate Scholarship and the FRQNT master’s scholarship. LP acknowledges
funding from NSERC Discovery Grant (NSERC RGPIN-2019-05771). TP acknowledges
financial support from the Fondation Courtois, and NSERC through the Discovery
Grants and Discovery Accelerator Supplement programs. MJF is supported by an
NSERC PDF and an RBC Post-Doctoral Fellowship.
